\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Remove duplication of phrase and shorten sentence.
Add "the"

The Joystream protocol is stateful, and the infrastructure for the secure distribution and updating of this state is a blockchain system.
A given instantiation of the Joystream protocol runs on its own single purpose blockchain infrastructure, which only processes transactions related to this instantiation. In the rest of the document this blockchain will be treated as a silent transaction ordering mechanism, but in what follows it is briefly described what assumptions are made about the blockchain infrastructure in the protocol design. In what follows, and in the rest of the document, the \textit{platform or platform state} will refer to the state upon which transactions operate. In Bitcoin, this would for example be the UTXO set. This would be as distinct from the state of the underlying blockchain infrastructure itself, namely the actual chain of blocks designated by the chain selection rule.

@@

The blockchain has a consensus algorithm in the classical BFT algorithm family, adapted to use Proof-of-Stake based voting power for a dynamic validator\footnote{We will refer to a block producing actor as a \textit{validator}, and anyone simply fully validating chain as a \textit{full validator}.} set. A designated platform token, described further in section \ref{sec:accounts_and_tokens}, is used by the validators to stake, and it is also the unit in which they are rewarded. There is a growing set of such consensus protocols \cite{tendermint, kiayias2017ouroboros, algorand}, and the following general properties of these systems are of importance to the protocol design.

>>>>

The Joystream protocol is stateful, and the infrastructure for the secure distribution and updating of this state is a blockchain system.
A given instantiation of the Joystream protocol runs on its own single purpose blockchain infrastructure, which only processes transactions related to this instantiation. In the rest of the document this blockchain will be treated as a silent transaction ordering mechanism, but in what follows it is briefly described what assumptions are made about the blockchain infrastructure in the protocol design. Here, and in the rest of the document, the \textit{platform or platform state} will refer to the state upon which transactions operate. In Bitcoin, this would for example be the UTXO set. This would be as distinct from the state of the underlying blockchain infrastructure itself, namely the actual chain of blocks designated by the chain selection rule.

@@

The blockchain has a consensus algorithm in the classical BFT algorithm family, adapted to use Proof-of-Stake based voting power for a dynamic validator\footnote{We will refer to a block producing actor as a \textit{validator}, and anyone simply fully validating the chain as a \textit{full validator}.} set. A designated platform token, described further in section \ref{sec:accounts_and_tokens}, is used by the validators to stake, and it is also the unit in which they are rewarded. There is a growing set of such consensus protocols \cite{tendermint, kiayias2017ouroboros, algorand}, and the following general properties of these systems are of importance to the protocol design.
